Research project title

### 2024-05-07 R0_journal/main.tex
paper update

\documentclass[smallextended]{./springer/svjour3}
\usepackage{graphicx} % This lets you include figures
\graphicspath{ {./figures/} }
\usepackage[rightcaption]{sidecap}
% \usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{imakeidx}
\usepackage{comment}
\usepackage{commath}
\usepackage[titletoc]{appendix}
\usepackage{graphicx}
\usepackage{resizegather}
\usepackage[english]{babel}
% \usepackage{subcaption}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{xfrac}
\usepackage{tabularx}
% \usepackage{amssymb}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage{verbatim}
% \usepackage{caption}
\usepackage{lscape}
\usepackage{relsize}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{breqn}
\usepackage{makecell}
\usepackage{longtable,tabularx}
\usepackage{multirow}
\usepackage{doi}
\usepackage{fancyhdr}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{setspace}
\usepackage{footnote}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue}}
\usepackage[numbers]{natbib}
\usepackage{mathtools}
%\usepackage[disable]{todonotes}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{booktabs,xcolor,siunitx}
\usepackage{soul}
% \usepackage{cleveref}
\usepackage[small, compact]{titlesec}
\usepackage{xcolor}
\usepackage{appendix}
% \usepackage{geometry}
% \geometry{
% a4paper,
% total={170mm,257mm},
% left=20mm,
% top=20mm,
% }

@@

Since heel strike (when the swing leg collides with the ground) is modeled as a perfectly inelastic 
collision, there is an instantaneous angular velocity change when heel stike occurs. Also, since the swing leg becomes the stance leg
after heel strike, the angles $x_1$ and $x_2$ must be switched in the mathematical model after each walking cycle. The transition matrices used to switch $x_1$ and $x_2$ as well 
as calculate the updated angular velocities after heel strike are shown in \ref{eq:trans1} and \ref{eq:trans2}, where $x^+$ represents the state
variable after heel strike and $x^-$ represents the state variable before impact, and $\mb{H}$ is the angular velocity transition matrix shown in the appendix.

@@

\begin{equation}
\label{eq:trans2}
\begin{bmatrix}
\\x_3^+\\
\\x_4^+\\
\end{bmatrix}
 = 
\mb{H}
\begin{bmatrix}
\\x_3^-\\
\\x_4^-\\
\end{bmatrix}
\end{equation}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=9cm]{./figures/onecycle.pdf}
\caption{One walking limit cycle of the compass gait. The swing leg makes a large swing (shown in blue, a large cicle) around while the stance leg only pivots (shown in orange.)}
\label{fig:onecycle}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=10cm]{./figures/states_onecycle.pdf}
\caption{States of the compas gait over time for one walking cycle.}
\label{fig:states_onecycle}
\end{figure}

@@

@@

>>>>

\documentclass{./springer/svjour3}
\usepackage{graphicx} % This lets you include figures
\graphicspath{ {./figures/} }
\usepackage[rightcaption]{sidecap}
% \usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{imakeidx}
\usepackage{comment}
\usepackage{commath}
\usepackage[titletoc]{appendix}
\usepackage{graphicx}
\usepackage{resizegather}
\usepackage[english]{babel}
% \usepackage{subcaption}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{xfrac}
\usepackage{tabularx}
% \usepackage{amssymb}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage{verbatim}
% \usepackage{caption}
\usepackage{lscape}
\usepackage{relsize}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{breqn}
\usepackage{makecell}
\usepackage{longtable,tabularx}
\usepackage{multirow}
\usepackage{doi}
\usepackage{fancyhdr}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{setspace}
\usepackage{footnote}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue}}
\usepackage[numbers]{natbib}
\usepackage{mathtools}
%\usepackage[disable]{todonotes}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{booktabs,xcolor,siunitx}
\usepackage{soul}
% \usepackage{cleveref}
\usepackage[small, compact]{titlesec}
\usepackage{xcolor}
\usepackage{appendix}
% \usepackage{geometry}
% \geometry{
% a4paper,
% total={170mm,257mm},
% left=20mm,
% top=20mm,
% }

@@

Since heel strike (when the swing leg collides with the ground) is modeled as a perfectly inelastic 
collision, there is an instantaneous angular velocity change when heel stike occurs. Also, since the swing leg becomes the stance leg
after heel strike, the angles $x_1$ and $x_2$ must be switched in the mathematical model after each walking cycle. The transition matrices used to switch $x_1$ and $x_2$ as well 
as calculate the updated angular velocities after heel strike are shown in \ref{eq:trans1} and \ref{eq:trans2}, where $x^+$ represents the state
variable after heel strike and $x^-$ represents the state variable before impact, $\mb{Q^-}$ and $\mb{Q^+}$ are the angular velocity transition matrices shown in the appendix.

@@

\begin{equation}
\label{eq:trans2}
\mb{Q^+}
\begin{bmatrix}
\\x_3^+\\
\\x_4^+\\
\end{bmatrix}
 = 
\mb{Q^-}
\begin{bmatrix}
\\x_3^-\\
\\x_4^-\\
\end{bmatrix}
\end{equation}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=10cm]{./figures/onecycle.pdf}
\caption{One walking limit cycle of the compass gait. The swing leg makes a large swing (shown in blue, a large cicle) around while the stance leg only pivots (shown in orange.)}
\label{fig:onecycle}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=9cm]{./figures/states_onecycle.pdf}
\caption{States of the compas gait over time for one walking cycle.}
\label{fig:states_onecycle}
\end{figure}

@@

\clearpage

@@

\clearpage
\appendix

\section{Compass Gait Equations}

Shown in this appendix is a more complete version of the dynamics equations of the compass gait. The swing stage dynamics can be written in standard planar manipulator 
dynamics form, shown in \ref{eq:swingeq}. The $\mb{M}$, $\mb{N}$, $\mb{G}$, and $\mb{U}$ matrices are also shown in \ref{eq:M}, \ref{eq:N}, \ref{eq:G}, and \ref{eq:U} respectively.

\begin{equation}
\label{eq:swingeq}
\mb{M(X)}\mb{\ddot{X}} + \mb{N(X, \dot{X})}\mb{\dot{X}} + \mb{G(X)} = \tau\mb{U}
\end{equation}

\begin{equation}
\mb{M} = 
\label{eq:M}
\begin{bmatrix}
\\mb^2 &  -mlbcos(x_2 - x_1)\\
\\-mlbcos(x_2 - x_1) &  m_{H}l^2 + m(l^2 + a^2)\\
\end{bmatrix}
\end{equation}

\begin{equation}
\mb{N} = 
\label{eq:N}
\begin{bmatrix}
\\0 &  mlb\dot{x_2}sin(x_2 - x_1)\\
\\-mlb\dot{x_1}sin(x_2 - x_1) &  0\\
\end{bmatrix}
\end{equation}

\begin{equation}
\mb{G} = 
\label{eq:G}
\begin{bmatrix}
\\mgbsin(x_1)\\
\\-(m_{H}l + m(a+l))gsin(x_2)\\
\end{bmatrix}
\end{equation}

\begin{equation}
\mb{U} = 
\label{eq:U}
\begin{bmatrix}
\\1\\
\\-1\\
\\0\\
\\0\\
\end{bmatrix}
\end{equation}

The transition equations when heel strike occurs are shown in \ref{eq:transeqn} and \ref{eq:transeqn2}, where $x^+$ signifies a state variables after heel strike and $x^-$ 
signals a state variable before
heel strike. The transition matrices $\mb{Q^+}$ and $\mb{Q^-}$ are shown in \ref{eq:Q-} and \ref{}. Note that $\alpha$ represents half the angle between the swing and stance 
legs.

\begin{equation}
\label{eq:transeqn}
\begin{bmatrix}
\\x_1^+\\
\\x_2^+\\
\end{bmatrix}
 = 
\begin{bmatrix}
0 & 1\\
1 & 0\\
\end{bmatrix}
\begin{bmatrix}
\\x_1^-\\
\\x_2^-\\
\end{bmatrix}
\end{equation}

\begin{equation}
\label{eq:transeqn2}
\mb{Q^+}
\begin{bmatrix}
\\x_3^+\\
\\x_4^+\\
\end{bmatrix}
= 
\mb{Q^-}
\begin{bmatrix}
\\x_3^-\\
\\x_4^-\\
\end{bmatrix}
\end{equation}

\begin{equation}
\mb{Q^-} = 
\label{eq:Q-}
\begin{bmatrix}
\\-mab & -mab + (m_Hl^2+2mal)cos(2\alpha)\\
\\0 & -mab\\
\end{bmatrix}
\end{equation}

\begin{equation}
\mb{Q^+} = 
\label{eq:Q+}
\begin{bmatrix}
\\mb(b-lcos(2\alpha)) & ml(l-bcos(2\alpha)) + ma^2 + m_Hl^2\\
\\mb^2 & -mblcos(2\alpha)\\
\end{bmatrix}
\end{equation}
